\textsf{Are frontier models superhuman chemists?}

### 2024-03-20 src/tex/appendix.tex
add main text radar
we need to create the heatmap on subsets

\begin{figure}
    \centering
    \includegraphics{figures/performance_per_topic.pdf}
    \caption{\textbf{Fraction of completely correctly answered questions per data source.} The heatmap shows, in color, the fraction of questions that were answered completely correctly by the models for each data source. The performance is measured as the fraction of questions that were answered completely correctly by the models. A score of 1 indicates that all questions were answered completely correctly, while a score of 0 indicates that none of the questions were answered completely correctly.}
    \label{fig:performance_per_topic}
    \script{analyze_performance_per_source.py}
\end{figure}

\begin{figure}
    \centering
    \includegraphics{figures/reading_ease_vs_model_performance.pdf}
    \caption{\textbf{Model performance as a function of reading ease.} The violinplots show the distribution of reading ease scores for questions that were answered completely correctly and those that were not. We do not observe a clear correlation between the reading ease of the questions and the performance of the models. }
    \script{reading_ease_vs_model_performance.py}
\end{figure}

>>>>

\begin{figure}[htb]
    \centering
    \includegraphics{figures/performance_per_topic.pdf}
    \caption{\textbf{Fraction of completely correctly answered questions per data source.} The heatmap shows, in color, the fraction of questions that were answered completely correctly by different systems for some of our data sources. The performance is measured as the fraction of questions that were answered completely correctly by the models. A score of one (red) indicates that all questions were answered completely correctly, while a score of zero (blue) indicates that none of the questions were answered completely correctly.
        We see that the performance of the models varies significantly between the different data sources. For instance, it is interesting to observe that questions sourced based on textbooks seem easier for our leading models than for humans. However, this performance does not correlate with performance on other sources, e.g., semi-programmatically created tasks such as questions about the number of peaks in an \gls{nmr} spectrum.
    }
    \label{fig:performance_per_topic}
    \script{analyze_performance_per_source.py}
\end{figure}

\begin{figure}[htb]
    \centering
    \includegraphics{figures/performance_per_topic_tiny.pdf}
    \caption{\textbf{Fraction of completely correctly answered questions per data source on the \enquote{tiny} subset.} The heatmap shows, in color, the fraction of questions that were answered completely correctly by different systems for some of our data sources. The performance is measured as the fraction of questions that were answered completely correctly by the models. A score of one (red) indicates that all questions were answered completely correctly, while a score of zero (blue) indicates that none of the questions were answered completely correctly.
        We see that the performance of the models varies significantly between the different data sources. For instance, it is interesting to observe that questions sourced based on textbooks seem easier for our leading models than for humans. However, this performance does not correlate with performance on other sources, e.g., semi-programmatically created tasks such as questions about the number of peaks in an \gls{nmr} spectrum.
    }
    \label{fig:performance_per_topic_tiny}
    \script{analyze_performance_per_source.py}
\end{figure}

\begin{figure}
    \centering
    \hspace*{-1cm}
    \includegraphics{figures/reading_ease_vs_model_performance.pdf}
    \caption{\textbf{Model performance as a function of reading ease.} The violinplots show the distribution of reading ease scores for questions that were answered completely correctly and those that were not. We do not observe a clear correlation between the reading ease of the questions and the performance of the models. }
    \script{reading_ease_vs_model_performance.py}
    \label{fig:reading_ease_vs_model_performance}
\end{figure}
